Dark matter halo shapes at $z=0$ in the Auriga simulations

### 2019-08-03 Document/paper.tex
update

% Abstract of the paper
\begin{abstract}
We present shape measurements of Milky Way sized dark matter halos at
redshift $z=0$ in a suite of 30 zoom simulations from the Auriga
project. 
We compare the results in full magnetohydrodynamics against dark
matter only simulations and find a strong influence of baryons 
in making dark matter haloes rounder at all radii compared to its dark 
matter only counterparts.
At distances $\lesssim 30$ kpc, rounder dark matter distributions
correlate with extended massive stellar discs and low core gas 
densities.  
We measure the alignment between the halo and the disc at
different radii and find a high degree of alignment at all radii for most 
of the galaxies.
In some cases the alignment significantly changes as a function of
radius implying that the halo shape twists; 
this effect correlates with extended stellar discs and
low gas densities and is almost absent in the dark matter only
simulations.  
In a comparison against observational constraints we find that $20\%$
of halos in our sample are consistent with observational results derived
from the Pal 5 stream that favor an almost spherical shape.
Including baryons is a required element to achieve this
level of agreement. In contrast, none of the simulations (dark matter
only nor with baryons) match the constrains derived from the
Sagittarius stream that favor an oblate dark matter halo.
\end{abstract}

@@

@@

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{correlations_twisting_triaxiality_MHD.pdf}
\end{center}
\caption{Twisting in the halo-disc alignment (measured as the standard deviation of the alignment angles)
  as a function of the halo triaxialiy at the radius indicated
  in each panel's title.
  The label with the $\rho$ value corresponds to the Spearmans rank
  correlation coefficient (mean value and error bars estimated via
  jackknife resampling) while the line shows the result of the
  minimum squares fit to the data.
  Twisting does not correlate with triaxility in the same way at every
  radii. The strongest correlation appears around $0.12R_{200}$ ($28\pm2$ kpc).} 
\label{fig:alignment_correlations}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{correlation_T_MHD_disc.pdf}
\end{center}
\caption{Correlations between the halo triaxility at different radii
  and baryonic disc properties. 
  The label with the $\rho$ value corresponds to the Spearmans rank
  correlation coefficient (mean value and error bars estimated via
  jackknife resampling).
  The line is the best minimum squares fit to a line.
  The x-axis in the first column is the gas density at the center of
  the galaxy with in a sphere of radius  $1$ kpc \citep{Pakmor17};
  the second column shows the disc to total mass ratio and the last
  column includes the disc optical radius defined to be the radius at which the
  $B$-band surface brightness drops below 25 mag arcsec$^{-2}$ \citep{auriga}.
  The largest correlations are found for the two smaller radii
  ($0.06R_{200}$ and $0.12R_{200}$).
  Extended and massive stellar discs with a low gas content at its
  core are correlated with low dark matter triaxilities.
  The correlation decreases as one approaches larger radii.}
\label{fig:disc_correlations}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{correlations_angles_alignment_MHD.pdf}
\end{center}
\caption{Twisting in the halo-disc alingment as a function of the same
  baryonic disc properties in Figure \ref{fig:disc_correlations}.
  The label with the $\rho$ value corresponds to the Spearmans rank
  correlation coefficient (mean value and error bars estimated via
  jackknife resampling).
  The line is the best minimum squares fit to a line.
  In this case the disc to total mass ratio does not correlate with the alignment twisting
  The gas density at the center and the disc optical radius still show
  a strong correlation, albeit weaker than what they had with the triaxility.}
\label{fig:twisting_correlations}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{correlations_ages_angles_alignment_MHD.pdf}
\end{center}
\caption{Twisting in the halo-disc alingment as a function of the
  mean stellar age in the bulge/disc and the lookback formation time of the
  dark matter halo (time at which it has half of its present mass).
  The label with the $\rho$ value corresponds to the Spearmans rank
  correlation coefficient (mean value and error bars estimated via
  jackknife resampling).
  The line is the best minimum squares fit to a line.}
\label{fig:twisting_age}
\end{figure*}

@@

Figure \ref{fig:resolution} shows the results for the six halos
available both at Level3 and Level4 resolutions.
The dotted lines compare the DMO simulations showing that down to
scales of $1$ kpc the two resolutions yield comparable results
\citep{VeraCiro11}. 
In MHD simulations the situation is different, as expected. 
With the exception of Au-27 the shape ratios $b/a$ and $c/a$ start
to differentiate from each other at radii smaller than $15$ kpc.
Above these radii, the differences between the triaxility values at
Level4 and Level3 in MHD simulations are small and never exceed $0.1$.
For this reason, in order to make the DM halo shape results comparable
in DMO and MHD simulations we only report measurements above $15$
kpc.}

@@

\subsection{Triaxiality}

@@

In some cases, the halo shape also twists in the presence of baryons, as opposed to
the situation in DMO simulations where the shape is coherent as a
function of radius.
In Figure \ref{fig:alignment_correlations2} we show the correlation
between twisting and the same baryonic properties that showed a high
degree of correlation with the triaxility.
In this case the disc to total ratio does not have a significant
degree of correlation.
Instead, the disc optical radius and the gas density at the core are
the most correlated. 
The correlation is such that extended stellar discs with a very low
gas density at its core show the most coherent halo shapes.

@@

\begin{table*}
  \centering 
  \begin{tabular}{c c c c c c c c c c c}
  \hline\hline
  Halo & $(b/a)_{16}$ & $(c/a)_{16}$& $(b/a)_{8}$ & $(c/a)_{8}$& $(b/a)_{4}$ & $(c/a)_{4}$& $(b/a)_{2}$ & $(c/a)_{2}$& $(b/a)_{1}$ & $(c/a)_{1}$ \\
  \hline
Au-1 & 0.48 & 0.41 & 0.52 & 0.44 & 0.59 & 0.48 & 0.66 & 0.53 & 0.72 & 0.55\\
Au-2 & 0.66 & 0.47 & 0.72 & 0.49 & 0.76 & 0.51 & 0.80 & 0.54 & 0.79 & 0.55\\
Au-3 & 0.56 & 0.42 & 0.61 & 0.47 & 0.70 & 0.55 & 0.79 & 0.65 & 0.85 & 0.72\\
Au-4 & 0.42 & 0.35 & 0.47 & 0.40 & 0.49 & 0.43 & 0.55 & 0.49 & 0.59 & 0.52\\
Au-5 & 0.49 & 0.41 & 0.53 & 0.47 & 0.56 & 0.51 & 0.59 & 0.56 & 0.66 & 0.59\\
Au-6 & 0.56 & 0.46 & 0.58 & 0.46 & 0.61 & 0.49 & 0.62 & 0.51 & 0.65 & 0.54\\
Au-7 & 0.46 & 0.37 & 0.45 & 0.37 & 0.51 & 0.40 & 0.55 & 0.41 & 0.62 & 0.46\\
Au-8 & 0.75 & 0.47 & 0.84 & 0.53 & 0.85 & 0.58 & 0.76 & 0.54 & 0.82 & 0.55\\
Au-9 & 0.49 & 0.40 & 0.52 & 0.43 & 0.54 & 0.45 & 0.60 & 0.52 & 0.65 & 0.60\\
Au-10 & 0.62 & 0.51 & 0.61 & 0.50 & 0.58 & 0.49 & 0.60 & 0.53 & 0.65 & 0.59\\
Au-11 & 0.47 & 0.37 & 0.36 & 0.29 & 0.32 & 0.28 & 0.41 & 0.37 & 0.47 & 0.45\\
Au-12 & 0.66 & 0.53 & 0.76 & 0.59 & 0.83 & 0.66 & 0.88 & 0.68 & 0.94 & 0.71\\
Au-13 & 0.60 & 0.52 & 0.61 & 0.53 & 0.64 & 0.54 & 0.70 & 0.56 & 0.73 & 0.54\\
Au-14 & 0.97 & 0.67 & 0.95 & 0.66 & 0.90 & 0.64 & 0.89 & 0.69 & 0.87 & 0.75\\
Au-15 & 0.61 & 0.42 & 0.65 & 0.48 & 0.68 & 0.52 & 0.66 & 0.50 & 0.70 & 0.54\\
Au-16 & 0.64 & 0.57 & 0.73 & 0.57 & 0.84 & 0.58 & 0.87 & 0.62 & 0.88 & 0.63\\
Au-17 & 0.98 & 0.79 & 0.98 & 0.83 & 0.95 & 0.84 & 0.91 & 0.81 & 0.93 & 0.87\\
Au-18 & 0.56 & 0.55 & 0.57 & 0.55 & 0.60 & 0.57 & 0.64 & 0.59 & 0.62 & 0.56\\
Au-19 & 0.58 & 0.51 & 0.59 & 0.50 & 0.65 & 0.54 & 0.73 & 0.61 & 0.80 & 0.70\\
Au-20 & 0.61 & 0.44 & 0.68 & 0.48 & 0.72 & 0.51 & 0.76 & 0.59 & 0.81 & 0.70\\
Au-21 & 0.67 & 0.50 & 0.75 & 0.50 & 0.81 & 0.61 & 0.80 & 0.66 & 0.74 & 0.64\\
Au-22 & 0.68 & 0.56 & 0.71 & 0.59 & 0.77 & 0.63 & 0.82 & 0.71 & 0.83 & 0.78\\
Au-23 & 0.54 & 0.41 & 0.58 & 0.44 & 0.62 & 0.49 & 0.70 & 0.57 & 0.77 & 0.66\\
Au-24 & 0.54 & 0.44 & 0.57 & 0.47 & 0.59 & 0.49 & 0.66 & 0.55 & 0.75 & 0.66\\
Au-25 & 0.59 & 0.56 & 0.66 & 0.65 & 0.71 & 0.66 & 0.62 & 0.55 & 0.69 & 0.61\\
Au-26 & 0.52 & 0.41 & 0.58 & 0.43 & 0.65 & 0.43 & 0.73 & 0.47 & 0.75 & 0.51\\
Au-27 & 0.53 & 0.45 & 0.61 & 0.51 & 0.68 & 0.56 & 0.76 & 0.62 & 0.84 & 0.64\\
Au-28 & 0.49 & 0.42 & 0.49 & 0.44 & 0.56 & 0.48 & 0.64 & 0.52 & 0.74 & 0.58\\
Au-29 & 0.50 & 0.40 & 0.56 & 0.45 & 0.61 & 0.48 & 0.69 & 0.54 & 0.72 & 0.60\\
Au-30 & 0.62 & 0.44 & 0.77 & 0.54 & 0.87 & 0.58 & 0.85 & 0.58 & 0.75 & 0.53\\
  \hline\hline
  \end{tabular}
  \caption{Dark matter halo axial ratios of Auriga galaxies at $z=0$ at
    different radii in DMO simulations. The subscripts $16$, $8$, $4$, $2$, $1$,
    indicate that the shape was measured at radii of $R_{200}/16$,
    $R_{200}/8$, $R_{200}/4$, $R_{200}/2$, $R_{200}$, respectively.   \label{table:DMO}}
\end{table*}

\begin{table*}
  \centering 
  \begin{tabular}{c c c c c c c c c c c}
  \hline\hline
  Halo & $(b/a)_{16}$ & $(c/a)_{16}$& $(b/a)_{8}$ & $(c/a)_{8}$& $(b/a)_{4}$ & $(c/a)_{4}$& $(b/a)_{2}$ & $(c/a)_{2}$& $(b/a)_{1}$ & $(c/a)_{1}$ \\
  \hline
Au-1 & 0.94 & 0.65 & 0.96 & 0.66 & 0.96 & 0.70 & 0.92 & 0.68 & 0.91 & 0.67\\
Au-2 & 0.93 & 0.61 & 0.95 & 0.58 & 0.96 & 0.61 & 0.96 & 0.65 & 0.88 & 0.65\\
Au-3 & 0.97 & 0.66 & 0.96 & 0.66 & 0.94 & 0.70 & 0.93 & 0.76 & 0.94 & 0.79\\
Au-4 & 0.88 & 0.77 & 0.82 & 0.79 & 0.80 & 0.76 & 0.85 & 0.79 & 0.83 & 0.76\\
Au-5 & 0.97 & 0.79 & 0.94 & 0.80 & 0.92 & 0.81 & 0.94 & 0.82 & 0.94 & 0.81\\
Au-6 & 0.98 & 0.60 & 0.96 & 0.60 & 0.92 & 0.63 & 0.86 & 0.63 & 0.78 & 0.61\\
Au-7 & 0.95 & 0.66 & 0.95 & 0.66 & 0.97 & 0.68 & 0.97 & 0.69 & 0.96 & 0.70\\
Au-8 & 0.99 & 0.59 & 0.97 & 0.62 & 0.92 & 0.66 & 0.76 & 0.57 & 0.83 & 0.58\\
Au-9 & 0.94 & 0.75 & 0.93 & 0.73 & 0.92 & 0.73 & 0.93 & 0.79 & 0.92 & 0.82\\
Au-10 & 0.95 & 0.85 & 0.94 & 0.85 & 0.93 & 0.85 & 0.92 & 0.82 & 0.91 & 0.80\\
Au-11 & 0.54 & 0.49 & 0.55 & 0.48 & 0.61 & 0.53 & 0.60 & 0.53 & 0.62 & 0.57\\
Au-12 & 0.95 & 0.77 & 0.88 & 0.81 & 0.90 & 0.84 & 0.92 & 0.81 & 0.95 & 0.82\\
Au-13 & 0.95 & 0.88 & 0.96 & 0.88 & 0.98 & 0.82 & 0.94 & 0.76 & 0.82 & 0.62\\
Au-14 & 0.95 & 0.75 & 0.93 & 0.79 & 0.91 & 0.80 & 0.91 & 0.79 & 0.93 & 0.81\\
Au-15 & 0.99 & 0.67 & 0.98 & 0.75 & 0.94 & 0.79 & 0.93 & 0.81 & 0.88 & 0.76\\
Au-16 & 0.99 & 0.69 & 0.99 & 0.70 & 0.99 & 0.74 & 0.98 & 0.76 & 0.99 & 0.99\\
Au-17 & 0.96 & 0.79 & 0.96 & 0.80 & 0.97 & 0.82 & 0.96 & 0.83 & 0.96 & 0.87\\
Au-18 & 0.93 & 0.76 & 0.92 & 0.74 & 0.86 & 0.72 & 0.81 & 0.71 & 0.74 & 0.66\\
Au-19 & 0.95 & 0.67 & 0.91 & 0.63 & 0.89 & 0.63 & 0.83 & 0.64 & 0.85 & 0.69\\
Au-20 & 0.81 & 0.58 & 0.91 & 0.64 & 0.95 & 0.71 & 0.97 & 0.78 & 0.86 & 0.77\\
Au-21 & 0.98 & 0.74 & 0.97 & 0.82 & 0.97 & 0.87 & 0.99 & 0.88 & 0.99 & 0.99\\
Au-22 & 0.96 & 0.84 & 0.93 & 0.84 & 0.93 & 0.85 & 0.95 & 0.87 & 0.97 & 0.88\\
Au-23 & 0.94 & 0.65 & 0.96 & 0.64 & 0.94 & 0.65 & 0.92 & 0.69 & 0.93 & 0.74\\
Au-24 & 0.99 & 0.67 & 1.00 & 0.63 & 0.99 & 0.65 & 0.97 & 0.68 & 0.98 & 0.70\\
Au-25 & 0.97 & 0.71 & 0.96 & 0.73 & 0.86 & 0.74 & 0.67 & 0.64 & 0.71 & 0.67\\
Au-26 & 0.96 & 0.76 & 0.97 & 0.73 & 0.97 & 0.70 & 0.99 & 0.68 & 0.97 & 0.67\\
Au-27 & 0.98 & 0.73 & 0.97 & 0.75 & 0.97 & 0.79 & 0.96 & 0.79 & 0.95 & 0.77\\
Au-28 & 0.98 & 0.82 & 0.94 & 0.77 & 0.88 & 0.73 & 0.86 & 0.74 & 0.93 & 0.75\\
Au-29 & 0.91 & 0.81 & 0.89 & 0.72 & 0.87 & 0.69 & 0.84 & 0.68 & 0.85 & 0.69\\
Au-30 & 0.89 & 0.73 & 0.78 & 0.64 & 0.69 & 0.53 & 0.80 & 0.58 & 0.91 & 0.63\\
  \hline\hline
  \end{tabular}

  \caption{Same as Table \ref{table:DMO} for MHD simulations.   \label{table:MHD}}
\end{table*}

@@

\appendix
\section{AS}
\label{appendix:physical}

>>>>

% Abstract of the paper
\begin{abstract}
We present shape measurements of Milky Way sized dark matter halos at
redshift $z=0$ in a suite of 30 zoom simulations from the Auriga
project. 
We compare the results in full magnetohydrodynamics against dark
matter only simulations and find a strong influence of baryons 
in making dark matter haloes rounder at all radii compared to its dark 
matter only counterparts.
At distances $\lesssim 30$ kpc, rounder dark matter distributions
correlate with extended massive stellar discs and low core gas 
densities.  
We measure the alignment between the halo and the disc at
different radii and find a high degree of alignment at all radii for most 
of the galaxies.
In some cases the alignment significantly changes as a function of
radius implying that the halo shape twists; 
this effect correlates with recently formed bulges and is almost
absent in the dark matter only simulations.  
In a comparison against observational constraints we find that $20\%$
of halos in our sample are consistent with observational results derived
from the Pal 5 stream that favor an almost spherical shape.
Including baryons is a required element to achieve this
level of agreement. In contrast, none of the simulations (dark matter
only nor with baryons) match the constrains derived from the
Sagittarius stream that favor an oblate dark matter halo.
\end{abstract}

@@

\begin{table*}
  \centering 
  \begin{tabular}{c c c c c c c c c c c}
  \hline\hline
  Halo & $(b/a)_{16}$ & $(c/a)_{16}$& $(b/a)_{8}$ & $(c/a)_{8}$& $(b/a)_{4}$ & $(c/a)_{4}$& $(b/a)_{2}$ & $(c/a)_{2}$& $(b/a)_{1}$ & $(c/a)_{1}$ \\
  \hline
Au-1 & 0.48 & 0.41 & 0.52 & 0.44 & 0.59 & 0.48 & 0.66 & 0.53 & 0.72 & 0.55\\
Au-2 & 0.66 & 0.47 & 0.72 & 0.49 & 0.76 & 0.51 & 0.80 & 0.54 & 0.79 & 0.55\\
Au-3 & 0.56 & 0.42 & 0.61 & 0.47 & 0.70 & 0.55 & 0.79 & 0.65 & 0.85 & 0.72\\
Au-4 & 0.42 & 0.35 & 0.47 & 0.40 & 0.49 & 0.43 & 0.55 & 0.49 & 0.59 & 0.52\\
Au-5 & 0.49 & 0.41 & 0.53 & 0.47 & 0.56 & 0.51 & 0.59 & 0.56 & 0.66 & 0.59\\
Au-6 & 0.56 & 0.46 & 0.58 & 0.46 & 0.61 & 0.49 & 0.62 & 0.51 & 0.65 & 0.54\\
Au-7 & 0.46 & 0.37 & 0.45 & 0.37 & 0.51 & 0.40 & 0.55 & 0.41 & 0.62 & 0.46\\
Au-8 & 0.75 & 0.47 & 0.84 & 0.53 & 0.85 & 0.58 & 0.76 & 0.54 & 0.82 & 0.55\\
Au-9 & 0.49 & 0.40 & 0.52 & 0.43 & 0.54 & 0.45 & 0.60 & 0.52 & 0.65 & 0.60\\
Au-10 & 0.62 & 0.51 & 0.61 & 0.50 & 0.58 & 0.49 & 0.60 & 0.53 & 0.65 & 0.59\\
Au-11 & 0.47 & 0.37 & 0.36 & 0.29 & 0.32 & 0.28 & 0.41 & 0.37 & 0.47 & 0.45\\
Au-12 & 0.66 & 0.53 & 0.76 & 0.59 & 0.83 & 0.66 & 0.88 & 0.68 & 0.94 & 0.71\\
Au-13 & 0.60 & 0.52 & 0.61 & 0.53 & 0.64 & 0.54 & 0.70 & 0.56 & 0.73 & 0.54\\
Au-14 & 0.97 & 0.67 & 0.95 & 0.66 & 0.90 & 0.64 & 0.89 & 0.69 & 0.87 & 0.75\\
Au-15 & 0.61 & 0.42 & 0.65 & 0.48 & 0.68 & 0.52 & 0.66 & 0.50 & 0.70 & 0.54\\
Au-16 & 0.64 & 0.57 & 0.73 & 0.57 & 0.84 & 0.58 & 0.87 & 0.62 & 0.88 & 0.63\\
Au-17 & 0.98 & 0.79 & 0.98 & 0.83 & 0.95 & 0.84 & 0.91 & 0.81 & 0.93 & 0.87\\
Au-18 & 0.56 & 0.55 & 0.57 & 0.55 & 0.60 & 0.57 & 0.64 & 0.59 & 0.62 & 0.56\\
Au-19 & 0.58 & 0.51 & 0.59 & 0.50 & 0.65 & 0.54 & 0.73 & 0.61 & 0.80 & 0.70\\
Au-20 & 0.61 & 0.44 & 0.68 & 0.48 & 0.72 & 0.51 & 0.76 & 0.59 & 0.81 & 0.70\\
Au-21 & 0.67 & 0.50 & 0.75 & 0.50 & 0.81 & 0.61 & 0.80 & 0.66 & 0.74 & 0.64\\
Au-22 & 0.68 & 0.56 & 0.71 & 0.59 & 0.77 & 0.63 & 0.82 & 0.71 & 0.83 & 0.78\\
Au-23 & 0.54 & 0.41 & 0.58 & 0.44 & 0.62 & 0.49 & 0.70 & 0.57 & 0.77 & 0.66\\
Au-24 & 0.54 & 0.44 & 0.57 & 0.47 & 0.59 & 0.49 & 0.66 & 0.55 & 0.75 & 0.66\\
Au-25 & 0.59 & 0.56 & 0.66 & 0.65 & 0.71 & 0.66 & 0.62 & 0.55 & 0.69 & 0.61\\
Au-26 & 0.52 & 0.41 & 0.58 & 0.43 & 0.65 & 0.43 & 0.73 & 0.47 & 0.75 & 0.51\\
Au-27 & 0.53 & 0.45 & 0.61 & 0.51 & 0.68 & 0.56 & 0.76 & 0.62 & 0.84 & 0.64\\
Au-28 & 0.49 & 0.42 & 0.49 & 0.44 & 0.56 & 0.48 & 0.64 & 0.52 & 0.74 & 0.58\\
Au-29 & 0.50 & 0.40 & 0.56 & 0.45 & 0.61 & 0.48 & 0.69 & 0.54 & 0.72 & 0.60\\
Au-30 & 0.62 & 0.44 & 0.77 & 0.54 & 0.87 & 0.58 & 0.85 & 0.58 & 0.75 & 0.53\\
  \hline\hline
  \end{tabular}
  \caption{Axial ratios of Auriga dark matter halos at $z=0$ at
    different radii in DMO simulations. The subscripts $16$, $8$, $4$, $2$, $1$,
    indicate that the shape was measured at radii of $R_{200}/16$,
    $R_{200}/8$, $R_{200}/4$, $R_{200}/2$, $R_{200}$, respectively.   \label{table:DMO}}
\end{table*}

\begin{table*}
  \centering 
  \begin{tabular}{c c c c c c c c c c c}
  \hline\hline
  Halo & $(b/a)_{16}$ & $(c/a)_{16}$& $(b/a)_{8}$ & $(c/a)_{8}$& $(b/a)_{4}$ & $(c/a)_{4}$& $(b/a)_{2}$ & $(c/a)_{2}$& $(b/a)_{1}$ & $(c/a)_{1}$ \\
  \hline
Au-1 & 0.94 & 0.65 & 0.96 & 0.66 & 0.96 & 0.70 & 0.92 & 0.68 & 0.91 & 0.67\\
Au-2 & 0.93 & 0.61 & 0.95 & 0.58 & 0.96 & 0.61 & 0.96 & 0.65 & 0.88 & 0.65\\
Au-3 & 0.97 & 0.66 & 0.96 & 0.66 & 0.94 & 0.70 & 0.93 & 0.76 & 0.94 & 0.79\\
Au-4 & 0.88 & 0.77 & 0.82 & 0.79 & 0.80 & 0.76 & 0.85 & 0.79 & 0.83 & 0.76\\
Au-5 & 0.97 & 0.79 & 0.94 & 0.80 & 0.92 & 0.81 & 0.94 & 0.82 & 0.94 & 0.81\\
Au-6 & 0.98 & 0.60 & 0.96 & 0.60 & 0.92 & 0.63 & 0.86 & 0.63 & 0.78 & 0.61\\
Au-7 & 0.95 & 0.66 & 0.95 & 0.66 & 0.97 & 0.68 & 0.97 & 0.69 & 0.96 & 0.70\\
Au-8 & 0.99 & 0.59 & 0.97 & 0.62 & 0.92 & 0.66 & 0.76 & 0.57 & 0.83 & 0.58\\
Au-9 & 0.94 & 0.75 & 0.93 & 0.73 & 0.92 & 0.73 & 0.93 & 0.79 & 0.92 & 0.82\\
Au-10 & 0.95 & 0.85 & 0.94 & 0.85 & 0.93 & 0.85 & 0.92 & 0.82 & 0.91 & 0.80\\
Au-11 & 0.54 & 0.49 & 0.55 & 0.48 & 0.61 & 0.53 & 0.60 & 0.53 & 0.62 & 0.57\\
Au-12 & 0.95 & 0.77 & 0.88 & 0.81 & 0.90 & 0.84 & 0.92 & 0.81 & 0.95 & 0.82\\
Au-13 & 0.95 & 0.88 & 0.96 & 0.88 & 0.98 & 0.82 & 0.94 & 0.76 & 0.82 & 0.62\\
Au-14 & 0.95 & 0.75 & 0.93 & 0.79 & 0.91 & 0.80 & 0.91 & 0.79 & 0.93 & 0.81\\
Au-15 & 0.99 & 0.67 & 0.98 & 0.75 & 0.94 & 0.79 & 0.93 & 0.81 & 0.88 & 0.76\\
Au-16 & 0.99 & 0.69 & 0.99 & 0.70 & 0.99 & 0.74 & 0.98 & 0.76 & 0.99 & 0.99\\
Au-17 & 0.96 & 0.79 & 0.96 & 0.80 & 0.97 & 0.82 & 0.96 & 0.83 & 0.96 & 0.87\\
Au-18 & 0.93 & 0.76 & 0.92 & 0.74 & 0.86 & 0.72 & 0.81 & 0.71 & 0.74 & 0.66\\
Au-19 & 0.95 & 0.67 & 0.91 & 0.63 & 0.89 & 0.63 & 0.83 & 0.64 & 0.85 & 0.69\\
Au-20 & 0.81 & 0.58 & 0.91 & 0.64 & 0.95 & 0.71 & 0.97 & 0.78 & 0.86 & 0.77\\
Au-21 & 0.98 & 0.74 & 0.97 & 0.82 & 0.97 & 0.87 & 0.99 & 0.88 & 0.99 & 0.99\\
Au-22 & 0.96 & 0.84 & 0.93 & 0.84 & 0.93 & 0.85 & 0.95 & 0.87 & 0.97 & 0.88\\
Au-23 & 0.94 & 0.65 & 0.96 & 0.64 & 0.94 & 0.65 & 0.92 & 0.69 & 0.93 & 0.74\\
Au-24 & 0.99 & 0.67 & 1.00 & 0.63 & 0.99 & 0.65 & 0.97 & 0.68 & 0.98 & 0.70\\
Au-25 & 0.97 & 0.71 & 0.96 & 0.73 & 0.86 & 0.74 & 0.67 & 0.64 & 0.71 & 0.67\\
Au-26 & 0.96 & 0.76 & 0.97 & 0.73 & 0.97 & 0.70 & 0.99 & 0.68 & 0.97 & 0.67\\
Au-27 & 0.98 & 0.73 & 0.97 & 0.75 & 0.97 & 0.79 & 0.96 & 0.79 & 0.95 & 0.77\\
Au-28 & 0.98 & 0.82 & 0.94 & 0.77 & 0.88 & 0.73 & 0.86 & 0.74 & 0.93 & 0.75\\
Au-29 & 0.91 & 0.81 & 0.89 & 0.72 & 0.87 & 0.69 & 0.84 & 0.68 & 0.85 & 0.69\\
Au-30 & 0.89 & 0.73 & 0.78 & 0.64 & 0.69 & 0.53 & 0.80 & 0.58 & 0.91 & 0.63\\
  \hline\hline
  \end{tabular}
  \caption{Same as Table \ref{table:DMO} for MHD simulations.   \label{table:MHD}}
\end{table*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{correlations_twisting_triaxiality_MHD.pdf}
\end{center}
\caption{Twisting in the halo-disc alignment (measured as the standard deviation of the alignment angles)
  as a function of the halo triaxialiy at the radius indicated
  in each panel's title.
  The label with the $\rho$ value corresponds to the Spearmans rank
  correlation coefficient (mean value and uncertainty estimated via
  jackknife resampling) while the line shows the result of the
  minimum squares fit to the data.
  Twisting does not correlate with triaxility in the same way at every
  radii. The strongest correlation appears around $0.12R_{200}$ ($28\pm2$ kpc).} 
\label{fig:alignment_correlations}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{correlation_T_MHD_disc.pdf}
\end{center}
\caption{Correlations between the halo triaxility at different radii
  and baryonic disc properties. 
  The label with the $\rho$ value corresponds to the Spearmans rank
  correlation coefficient (mean value and uncertainty estimated via
  jackknife resampling).
  The line is the best minimum squares fit to a line.
  The x-axis in the first column is the gas density at the center of
  the galaxy with in a sphere of radius  $1$ kpc \citep{Pakmor17};
  the second column shows the disc to total mass ratio and the last
  column includes the disc optical radius defined to be the radius at which the
  $B$-band surface brightness drops below 25 mag arcsec$^{-2}$ \citep{auriga}.
  The largest correlations are found for the two smaller radii
  ($0.06R_{200}$ and $0.12R_{200}$).
  Extended and massive stellar discs with a low gas content at its
  core are correlated with low dark matter triaxilities.
  The correlation decreases as one approaches larger radii.}
\label{fig:disc_correlations}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{correlations_angles_alignment_MHD.pdf}
\end{center}
\caption{Twisting in the halo-disc alingment as a function of the same
  baryonic disc properties in Figure \ref{fig:disc_correlations}.
  The label with the $\rho$ value corresponds to the Spearmans rank
  correlation coefficient (mean value and uncertainty estimated via
  jackknife resampling).
  The line is the best minimum squares fit to a line.
  In this case the disc to total mass ratio does not correlate with the alignment twisting
  The gas density at the center and the disc optical radius still show
  a strong correlation, albeit weaker than what they had with the triaxility.}
\label{fig:twisting_correlations}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{correlations_ages_angles_alignment_MHD.pdf}
\end{center}
\caption{Twisting in the halo-disc alingment as a function of the
  mean stellar age in the bulge/disc and the lookback formation time of the
  dark matter halo (time at which it has half of its present mass).
  The label with the $\rho$ value corresponds to the Spearmans rank
  correlation coefficient (mean value and uncertainty estimated via
  jackknife resampling).
  The line is the best minimum squares fit to a line.}
\label{fig:twisting_age}
\end{figure*}

@@

Figure \ref{fig:resolution} shows the results for the six halos
available both at Level3 and Level4 resolutions.
The dotted lines compare the DMO simulations showing that down to
scales of $1$ kpc the two resolutions yield comparable results
\citep{VeraCiro11}. 
In MHD simulations the situation is different, as expected. 
The shape ratios $b/a$ and $c/a$ start to differentiate
from each other at radii smaller than $15$ kpc, tith the exception of
Au-27 that shows a good agreement in the shape measuremnts at all radii, 
Above $15$ kpc, the differences between the triaxility values at
Level4 and Level3 in MHD simulations are small and never exceed $0.1$. 
For this reason, in order to make the DM halo shape results comparable
in DMO and MHD simulations we only report measurements above $15$
kpc.}

@@

{\bf The main measurements are summarized in Table \ref{table:DMO} for the
DMO simulations and Table \ref{table:MHD} for the MHD simulations.
These results are computed at five different radii $R_{200}/16$,
$R_{200}/8$, $R_{200}/4$, $R_{200}/2$ and $R_{200}$.
In the following subsections we present and comment in greater detail
the results for the triaxility, the halo-disc alignment and the
correlations with baryonic disc properties.}

\subsection{Triaxility}

@@

In some cases, the halo shape also twists in the presence of baryons, as opposed to
the situation in DMO simulations where the shape is coherent as a
function of radius.
In Figure \ref{fig:twisting_correlations} we show the correlation
between twisting and the same baryonic properties that showed a high
degree of correlation with the triaxility.
In this case the disc to total ratio does not have a significant
degree of correlation.
Instead, the disc optical radius and the gas density at the core are
the most correlated. 
The correlation is such that extended stellar discs with a very low
gas density at its core show the most coherent halo shapes.

{\bf Recently \cite{2017MNRAS.469..594B} reported that MW-like DM haloes can
be roughly splint into two distinct families: stalled and accreting.
Stalled haloes assembled early and have remained almost unchanged
in the last $7$ Gyr, while accreting halos have been growing
constantly.
\cite{2017MNRAS.469..594B} also link this dicotomy to the dark matter
filaments feeding the halos. 
Stalled halos at $z=0$ are embbeded in a single large thick filament, while
accreting halos are pierced by many thinner filaments. 
To what extent the twisting and high triaxility present in the MHD
halos can be linked to this dicotomy?
In Figure \ref{fig:twisting_age} we show the correlation between the
twisting and the age of the bulge, the age of the stellar disc and the
DM halo formation redshift. 
The ages are estimated directly as the mean value in the stellar age
distribution for each component, while the formation redshift is
defined as the redshif at which the halo already has half of its $z=0$
mass. 
In the three cases we find a correlation between ages and twisting
that goes in the direction claimed by \cite{2017MNRAS.469..594B}:
components with early assembly (i.e. stalled) have a smaller degree of
twisting.
A detailed study with respect to the cosmic web location is beyond the
scope of our paper.}

@@

@@
